% SPDX-License-Identifier: CC-BY-SA-4.0
% Copyright (C) 2019 Eric Herman <eric@freesa.org>
% handy link: http://sage5e.wikidot.com/subclass:arcane-trickster
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{ArcaneTrickster Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raggedright
\newcommand{\DndArcaneTricksterSpellSlotsFirst}{
	\ifthenelse{\DndArcaneTricksterLevel < 3}{0}{
	\ifthenelse{\equal{\DndArcaneTricksterLevel}{3}}{2}{
	\ifthenelse{\DndArcaneTricksterLevel < 7}{3}{4}}}}

\newcommand{\DndArcaneTricksterSpellSlotsSecond}{
	\ifthenelse{\DndArcaneTricksterLevel < 7}{0}{
	\ifthenelse{\DndArcaneTricksterLevel < 10}{2}{3}}}

\newcommand{\DndArcaneTricksterSpellSlotsThird}{
	\ifthenelse{\DndArcaneTricksterLevel < 13}{0}{
	\ifthenelse{\DndArcaneTricksterLevel < 16}{2}{3}}}

\newcommand{\DndArcaneTricksterSpellSlotsFourth}{
	\ifthenelse{\DndArcaneTricksterLevel < 19}{0}{1}}

\begin{tabular}{|c|c|c|}
\hline
Spellcasting Ability: &
Spell save DC: &
Spell Attack bonus \\
{\huge \DndCastingStatName} &
{\huge \DndSpellSaveDC} &
{\huge \ifthenelse{\DndStrMod<0}{}{+}\DndSpellAttackMod} \\
\hline
\end{tabular}

\begin{multicols}{3}
{\scriptsize
When you reach 3rd level, you gain the ability to cast spells. See
chapter 10 for the general rules of spellcasting and chapter 11 for the
wizard spell list.\par
\vspace{1em}\hrule\vspace{1em}
\textbf{Cantrips}: You learn three cantrips: \textit{mage hand} and two
other cantrips of your choice from the wizard spell list. you learn
another cantrip of your choice at 10th level.
\vspace{1em}\hrule\vspace{1em}
\textbf{Spell Slots}: The Arcane Trickster Spellcasting table shows how
many spell slots you have to cast your spells of 1st level and higher.
To cast one of these spells, you must expend a slot of the spell's level
or higher. You greain all expended spell slots when you finish a long
rest.
\par
For example, if you know the 1st-level spell \textit{charm person} and
have a 1st-level and a 2nd-level spell slot available, you can cast
\textit{charm person} using either slot.
\vspace{1em}\hrule\vspace{1em}
\textbf{Spells Known of 1st-Level and Higher}: You know three 1st-level
wizard spells of your choice, two of which you must choose for the
enchantment and illusion spells on the wizard spell list.\par
The Spells Known column of the Arcane Trickster Spellcasting table shows
when you learn more wizard spells of 1st level or higher. Each of these
spells must be an enchantment or illusion spell of your choice, and must
be of a level for which you have spell slots. For instance, when you
reach 7th level in this class, you can learn one new spell of 1st or 2nd
level.\par
The spells you learn at 8th, 14th, and 20th level can come from any
school of magic.\par
Whenever you gain a level in this class, you can replace one of the
wizard spells you know with another spell of your choice from the
wizard spell list. The new spell must be of a level for which you have
spell slots, and it must be an enchantment or illusion spell unless
you're replacing the spell you gained at 8th, 14th, or 20th level.\par
} %scriptsize
\end{multicols}
\par
\fbox{ \parbox{\textwidth}{
\textbf{Mage Hand Legerdemain}:
Starting at 3rd level, when you cast \textit{mage hand}, you can make
the spectral hand invisible, and you can perform the following
additional tasks with it:
\begin{itemize}
\item You can stow one obect the hand is holding in a container worn or
	carried by another creature.
\item You can retrieve an object in a container worn or carried by
	another creature.
\item You can use thieves' tools to pick locks and tisarm traps at
	range.
\end{itemize}
You can perform one of these tasks without being noticed by a creature
if you succeed on a Dexterity (Slight of Hand) check contested by the
creature's Wisdom (Perception) check.\par
In addition, you can use the bonus action granted by your Cunning
Action to control the hand.\par
}}
\vspace{1em}
\vspace{1em}

\ovalbox{
\begin{tabular}{c}
	\ovalbox{\DndArcaneTricksterSpellSlotsFirst} \nth{1} level slots \\
	\framebox(60,50){} \\
\end{tabular}
\begin{tabular}{c}
	\ovalbox{\DndArcaneTricksterSpellSlotsSecond} \nth{2} level slots \\
	\framebox(60,50){} \\
\end{tabular}
\begin{tabular}{c}
	\ovalbox{\DndArcaneTricksterSpellSlotsThird} \nth{3} level slots \\
	\framebox(60,50){} \\
\end{tabular}
\begin{tabular}{c}
	\ovalbox{\DndArcaneTricksterSpellSlotsFourth} \nth{4} level slots \\
	\framebox(60,50){} \\
\end{tabular}
}

\vspace{1em}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ArcaneTrickster spell table
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\scriptsize
\begin{tabular}{|r l l l r l l l|}
\hline
Lvl &
Name &
VSM &
Cast Time &
Duration &
Range &
Save &
\\

0 &
Mage hand &
V, S &
Action &
1 Minute &
30 ft &
&
\\


0 &
Mold earth &
S &
Action &
Instantaneous/1 hour &
30 ft &
&
\\

\hline

1 &
Silent image &
V, S, M &
Action &
10 minutes &
60 ft &
&
Concentration \\


1 &
Disguise self &
V, S &
Action &
1 Hour &
Self &
&
\\


1 &
Find familiar &
V, S, M &
1 Hour &
&
10 ft &
&
\\


1 &
Charm person &
V, S &
Action &
1 Hour &
30 ft &
&
\\

\hline
\end{tabular}

} % scriptsize
