% SPDX-License-Identifier: CC-BY-SA-4.0
% sheet-kais.tex: A LaTeX (pure-text, git-friendly) D&D5e character sheet
% Copyright (C) 2019 Eric Herman <eric@freesa.org>
% For license see:
% * https://creativecommons.org/licenses/by-sa/4.0/legalcode
% See also the Open Game License and Frequently Asked Questions page:
% * https://roll20.net/compendium/dnd5e/Miscellaneous:License
% * https://www.wizards.com/default.asp?x=d20/oglfaq/20040123f
%
\documentclass{article}
\title{Dungeons \& Dragons 5e character sheet}
\date{2019-12-29}
\author{Eric Herman}
\usepackage[a4paper,margin=1cm]{geometry}
\input{dnd-required-packages}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin input basic variables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\DndPlayer}{Ace}
\newcommand{\DndName}{Kais Foxglove}
\newcommand{\DndClass}{Rogue/Trickster}
\FPeval{\DndLevel}{6}
\newcommand{\DndBackground}{Outlander}
\newcommand{\DndRace}{Wood elf}
\newcommand{\DndAlignment}{Neutral Evil}
% \newcommand{\DndXP}{}
\newcommand{\DndAge}{100 years}
\newcommand{\DndHeight}{6'}
\newcommand{\DndWeight}{160 lbs}
% \newcommand{\DndEyes}{}
% \newcommand{\DndSkin}{}
% \newcommand{\DndHair}{}

% 4th level ability score improvements included
\FPeval{\DndStr}{15} %
\FPeval{\DndDex}{16 + 2} % (+2 Elf)
\FPeval{\DndCon}{13 + 1} % (4th level Tavern Brawler)
\FPeval{\DndInt}{14} %
\FPeval{\DndWis}{16 + 1} % (+1 Wood Elf)
\FPeval{\DndCha}{9} %

\FPeval{\DndArmorClass}{16}
\FPeval{\DndSpeed}{35} % Wood Elf
\FPeval{\DndHitDie}{8}

% stat proficiences: \FPeval{\DndIsProficientStr}{1} for proficient
\FPeval{\DndIsProficientDex}{1} % Rogue
\FPeval{\DndIsProficientInt}{1} % Rogue

% skill proficiences: e.g.: \FPeval{\DndIsProficientSlightOfHand}{1}
\FPeval{\DndIsProficientAcrobatics}{1} % Rogue
\FPeval{\DndIsProficientAthletics}{1} % Outlander
\FPeval{\DndIsProficientInsight}{1} % Rogue
\FPeval{\DndIsProficientPerception}{1} % Elf "Keen Senses"
\FPeval{\DndIsProficientSlightOfHand}{1} % Rogue
\FPeval{\DndIsProficientStealth}{1} % Rogue
\FPeval{\DndIsProficientSurvival}{1} % Outlander

\FPeval{\DndIsExpertisePerception}{1} % Rogue 1st
\FPeval{\DndIsExpertiseInsight}{1} % Rogue 6th
\FPeval{\DndIsExpertiseStealth}{1} % Rogue 6th

% stat for spellcasting: e.g.: \FPeval{\DndIsSpellcasterInt}{1}
% dual-stat spellcasting (e.g.: multiclass INT, CHA) not supported
\FPeval{\DndIsSpellcasterInt}{1}
\FPeval{\DndArcaneTricksterLevel}{\DndLevel}

\newcommand{\DndPersonalityTraits}{
I hide food and trinkets in my pockets.
}
\newcommand{\DndIdeals}{
All people, rich or poor, deserve respect.
}
\newcommand{\DndBonds}{
My clan is the most important thing in my life, even though they are far
from me.
}
\newcommand{\DndFlaws}{
It's not stealing if someone else needs it more.
}

\newcommand{\DndOtherPoficienciesAndLanguages}{
\emph{Languages}: Elvish, Common\par
\emph{Weapon Proficiencies}: Improvised Weapons, Simple Weapons, Crossbow hand, Longsword, Rapier, Shortsword, Shortbow, Longbow\par
\emph{Armor Proficiencies}: Light Armor\par
\emph{Tools}: Thieves' tools, Lute, Thieves lantern\par
\emph{Expertise}: Thieves' tools\par
\emph{Roguish Archetype}: Arcane Trickster\par
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% background features
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndBackgroundFeatureOne}{
\textbf{Wanderer}: You have an excellent memory for maps and geography,
and can always recall the general laoout of terrain, settlements, and
other features around you. In addition, you can find food and fresh
water for yourself and up to five other people each day, provided that
the land offers berries, small game, water, and so forth.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Race abilities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndRaceSpecialOne}{
\textbf{Darkvision}: Accustomed to twilit forests and the night sky, you
have superior vision in dark and dim Conditions. You can see in dim
light within 60 feet of you as if it were bright light, and in Darkness
as if it were dim light. You can't discern color in Darkness, only
shades of gray.
}

\newcommand{\DndRaceSpecialTwo}{
\textbf{Fey Ancestry}: You have advantage on Saving Throws against being
Charmed, and magic can't put you to sleep.
}

\newcommand{\DndRaceSpecialThree}{
\textbf{Trance}:  Elves don't need to sleep. Instead, they meditate
deeply, remaining semiconscious, for 4 hours a day. (The Common word for
such meditation is "trance".) While meditating, you can dream after a
fashion; such dreams are actually mental exercises that have become
reflexive through years of practice. After Resting in this way, you gain
the same benefit that a human does from 8 hours of sleep.
}

\newcommand{\DndRaceSpecialFour}{
\textbf{Mask of the Wild}:
You can attempt to hide even when you are only lightly obscured by
foliage, heavy rain, falling snow, mist, and other natural phenomena.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Class abilities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndClassAbilityOne}{\textbf{Sneak Attack}:
Beginning at 1st level, you know how to strike subtly and exploit a
foe's distraction. Once per turn, you can deal an extra 1d6 damage to
one creature you hit with an Attack if you have advantage on the Attack
roll. The Attack must use a Finesse or a ranged weapon.
\par
You don't need advantage on the Attack roll if another enemy of the
target is within 5 feet of it, that enemy isn't Incapacitated, and you
don't have disadvantage on the Attack roll.
\par
The amount of the extra damage increases as you gain levels in this
class, as shown in the Sneak Attack column of the Rogue table.
}

\newcommand{\DndClassAbilityTwo}{\textbf{Thieves' Cant}:
During your rogue Training you learned thieves' cant, a Secret mix of
dialect, jargon, and code that allows you to hide messages in seemingly
normal conversation. Only another creature that knows thieves' cant
understands such messages. It takes four times longer to convey such a
Message than it does to speak the same idea plainly.
\par
In addition, you understand a set of Secret signs and symbols used to
convey short, simple messages, such as whether an area is dangerous or
the territory of a thieves' guild, whether loot is nearby, or whether
the people in an area are easy marks or will provide a Safe House for
thieves on the run.
}

\newcommand{\DndClassAbilityThree}{\textbf{Cunning Action}:
Starting at 2nd level, your quick thinking and agility allow you to move
and act quickly. You can take a Bonus Action on each of your turns in
Combat. This action can be used only to take the Dash, Disengage, or
Hide action.
}

% Tavern Brawler feat taken at 4th level instead of ability score
% improvement
\newcommand{\DndClassAbilityFour}{\textbf{Tavern Brawler}:
Accustomed to rough-and-tumble fighting using whatever weapons happen to
be at hand, you gain the following benefits: Increase your Strength or
Constitution score by 1 to a maximum of 20 (included). You are
proficient with improvised weapon weapons. Your unarmed strike uses a d4
for damage. When you hit a creature with an unarmed strike or an
improvised weapon on your turn, you can use a bonus action to attempt to
grapple the target.
}

\newcommand{\DndClassAbilityFive}{\textbf{Uncanny Dodge}:
Starting at 5th level, when an attacker that you can see hits you with
an Attack, you can use your Reaction to halve the attack's damage
against you.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Specialty
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newcommand{\DndSpecialtyName}{Arcane Trickster}
% \newcommand{\DndSpecialtyPreamble}{}
% \newcommand{\DndSpecialtyAbilityOne}{\textbf{foo}:bar}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Attacks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndWeaponOneName}{Rapier}
\newcommand{\DndWeaponOneType}{Dex}
\newcommand{\DndWeaponOneDamageType}{piercing}
\newcommand{\DndWeaponOneDamage}{1d8}

\newcommand{\DndWeaponTwoName}{Longbow}
\newcommand{\DndWeaponTwoType}{Dex}
\newcommand{\DndWeaponTwoDamageType}{piercing}
\newcommand{\DndWeaponTwoDamage}{1d8}

\newcommand{\DndWeaponThreeName}{shortsword}
\newcommand{\DndWeaponThreeType}{Dex}
\newcommand{\DndWeaponThreeDamageType}{piercing}
\newcommand{\DndWeaponThreeDamage}{1d6}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Combat Special (box highlight)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newcommand{\DndCombatSpecialOne}{\textbf{foo}: bar}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Class Specialty (box highlight)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newcommand{\DndSpecialtyBoxHighlightOne}{}

% Note: Inventory is in a separate sheet document entirely

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% pull in all of the variables needed for everything else
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{dnd-ensure-variables}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End of global variables, beginning of layout
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fonts are hard, going with Alegreya for now:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[T1]{fontenc}
\usepackage{Alegreya} %% Option 'black' gives heavier bold face
\renewcommand*\oldstylenums[1]{{\AlegreyaOsF #1}} % cargo culting
\setlength\parindent{0pt} % we do not want to repeat \noindent everwhere
\begin{document}
\pagenumbering{gobble} % turn off pagenumbers
\newpage
\raggedright
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Page 1: character sheet header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{dnd-character-header-1}
\input{dnd-main-stats-and-traits}
% end stats, begin regular text-like layout
%\input{dnd-combat-special}
\input{dnd-class-abilities}
\input{dnd-special-abilites}
\input{dnd-background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Page 2: character physical stuff header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\raggedright
\input{dnd-character-header-2}
\input{dnd-race-abilities}
\input{dnd-trickster-spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
