% SPDX-License-Identifier: CC-BY-SA-4.0
% sheet-autun.tex: A LaTeX (pure-text, git-friendly) D&D5e character sheet
% Copyright (C) 2019 Eric Herman <eric@freesa.org>
% For license see:
% * https://creativecommons.org/licenses/by-sa/4.0/legalcode
% See also the Open Game License and Frequently Asked Questions page:
% * https://roll20.net/compendium/dnd5e/Miscellaneous:License
% * https://www.wizards.com/default.asp?x=d20/oglfaq/20040123f
% And:
% * https://roll20.net/compendium/dnd5e/Paladin
% * https://dnd5e.wikidot.com
% * https://dnd-wiki.org/wiki/SRD5:Paladin
% * https://merovia.obsidianportal.com
%
\documentclass{article}
\title{Dungeons \& Dragons 5e character sheet}
\date{2019-12-29}
\author{Eric Herman}
\usepackage[a4paper,margin=1cm]{geometry}
\input{dnd-required-packages}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin input basic variables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\DndPlayer}{Eric}
\newcommand{\DndName}{Autun}
\newcommand{\DndTitle}{Warden of Cantos Wood}
\newcommand{\DndClass}{Paladin}
\FPeval{\DndLevel}{8}
\newcommand{\DndBackground}{Acolyte}
\newcommand{\DndRace}{Firbolg}
\newcommand{\DndAlignment}{Neutral Good}
\newcommand{\DndXP}{}
\newcommand{\DndAge}{29 (adolescent adult)}
\newcommand{\DndHeight}{221cm (7'3")}
\newcommand{\DndWeight}{88kg (195lb)}
\newcommand{\DndEyes}{green-brown}
\newcommand{\DndSkin}{blue-green}
\newcommand{\DndHair}{brown}

\FPeval{\DndStr}{18 + 1 + 1} % firbolg, 4th
\FPeval{\DndDex}{12}
\FPeval{\DndCon}{13 + 2} % 8th
\FPeval{\DndInt}{10}
\FPeval{\DndWis}{12 + 2} % firbolg
\FPeval{\DndCha}{15 + 1} % 4th

\FPeval{\DndArmorClass}{17}
\FPeval{\DndSpeed}{30}
\FPeval{\DndHitDie}{10}

% Aura of Protection grants ChaMod
\FPeval{\DndSaveMod}{clip(trunc((\DndCha / 2), 0) - 5)}

% stat proficiences: \FPeval{\DndIsProficientStr}{1} for proficient
\FPeval{\DndIsProficientWis}{1}
\FPeval{\DndIsProficientCha}{1}

% skill proficiences: e.g.: \FPeval{\DndIsProficientSlightOfHand}{1}
\FPeval{\DndIsProficientAthletics}{1} % Paladin
\FPeval{\DndIsProficientInsight}{1} % Acolyte
\FPeval{\DndIsProficientMedicine}{1} % Paladin
\FPeval{\DndIsProficientReligion}{1} % Acolyte

% stat for spellcasting: e.g.: \FPeval{\DndIsSpellcasterInt}{1}
% dual-stat spellcasting (e.g.: multiclass INT, CHA) not supported
\FPeval{\DndIsSpellcasterCha}{1}
\FPeval{\DndPaladinLevel}{\DndLevel}

\newcommand{\DndPersonalityTraits}{
I see omens in every event and action. The Gods try to speak to us,
we just need to listen.
}
\newcommand{\DndIdeals}{
I always try to help those in need, no matter what the personal cost.
}
\newcommand{\DndBonds}{
I will do anything to protect the forests, for they are Her temples.
}
\newcommand{\DndFlaws}{
My piety sometimes leads me to blindly trust those that profess faith
in my god.
}

\newcommand{\DndOtherPoficienciesAndLanguages}{
\emph{Firbolg ability score increase}: +2 Wisdom, +1 Strength (included)\par
\emph{Languages}: Common, Elvish. (not Giant; backstory)\par
\emph{Acolyte Proficiencies}: Insight, Religion\par
\emph{Paladin Skills}: Athletics, Medicine\par
\emph{Armor Proficiencies}: Light Armor, Medium Armor, Heavy Armor, Shields\par
\emph{Weapon Proficiencies}: Simple Weapons, Martial Weapons\par
\emph{Ability Score Improvement}: +1 STR, +1 CHA (included)\par
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Race abilities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndRaceSpecialOne}{
\textbf{Firbolg Magic}: You can cast \textit{Detect Magic} and
\textit{Disguise Self} with this trait, using Wisdom as your
spellcasting ability for them. Once you cast either spell, you can't
cast it again until you finish a short or long rest. When you use this
version of \textit{Disguise Self}, you can seem up to 3 feet shorter
than normal, allowing you to more easily blend in with humans and elves.
}
\newcommand{\DndRaceSpecialTwo}{
\textbf{Firbolg Hidden Step}: As a bonus action, you can magically turn
invisible until the start of your next turn or until you attack, make a
damage roll, or force someone to make a saving throw. Once you use this
trait, you can't use it again until you finish a short or long rest.
}
\newcommand{\DndRaceSpecialThree}{
\textbf{Firbolg Powerful Build}: You count as one size larger when
determining your carrying capacity and the weight you can push, drag, or
lift.
}
\FPeval{\DndSizeLiftFactor}{2}
\newcommand{\DndRaceSpecialFour}{
\textbf{Speech of Beast and Leaf}: You have the ability to communicate
in a limited manner with beasts and plants. They can understand the
meaning of your words, though you have no special ability to understand
them in return. You have advantage on all Charisma checks made to
influence them.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% background features
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndBackgroundFeatureOne}{
\textbf{Shelter of the Faithful}:
As an acolyte, you command the respect of those who share your faith,
and you can perform the religious ceremonies of your deity. You and your
adventuring companions can expect to receive free healing and care at a
temple, shrine, or ther established presence of your faith, though you
must provide any material components needed for spells. Those who share
your religion will support you (but only you) at a modest lifestyle.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Class abilities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndClassAbilityOne}{\textbf{Divine Sense}:
The presence of strong evil registers on your Senses like a noxious
odor, and powerful good rings like heavenly music in your ears. As an
action, you can open your awareness to detect such forces. Until the end
of your next turn, you know the location of any Celestial, fiend, or
Undead within 60 feet of you that is not behind total cover. You know
the type (celestial, fiend, or undead) of any being whose presence you
sense, but not its identity (the Vampire Count Strahd von Zarovich, for
instance). Within the same radius, you also detect the presence of any
place or object that has been consecrated or desecrated, as with the
Hallow spell.\par
You can use this feature a number of times equal to 1 + your Charisma
modifier. When you finish a Long Rest, you regain all expended uses.
}
\newcommand{\DndClassAbilityTwo}{\textbf{Lay on Hands}:
Your blessed touch can heal wounds. You have a pool of Healing power
that replenishes when you take a Long Rest. With that pool, you can
restore a total number of Hit Points equal to your Paladin level x 5.
\par
As an action, you can touch a creature and draw power from the pool to
restore a number of Hit Points to that creature, up to the maximum
amount remaining in your pool.
\par
Alternatively, you can expend 5 Hit Points from your pool of Healing to
cure the target of one disease or neutralize one poison affecting it.
You can cure multiple Diseases and neutralize multiple Poisons with a
single use of Lay on Hands, expending Hit Points separately for each
one.
\par
This feature has no effect on Undead and constructs.
}
\newcommand{\DndClassAbilityThree}{\textbf{Great Weapon Fighting}:
When you roll a 1 or 2 on a damage die for an Attack you make with a
melee weapon that you are wielding with two hands, you can reroll the
die and must use the new roll. The weapon must have the Two-Handed or
Versatile property for you to gain this benefit.
}
\newcommand{\DndClassAbilityFour}{\textbf{Divine Smite}:
Starting at 2nd level, when you hit a creature with a melee weapon
Attack, you can expend one spell slot to deal radiant damage to the
target, in addition to the weapon's damage. The extra damage is 2d8 for
a 1st-level spell slot, plus 1d8 for each Spell Level higher than 1st,
to a maximum of 5d8. The damage increases by 1d8 if the target is an
Undead or a fiend.
}
\newcommand{\DndClassAbilityFive}{\textbf{Divine Health}:
By 3rd level, the Divine Magic flowing through you makes you immune to
disease.
}
\newcommand{\DndClassAbilitySix}{\textbf{Extra Attack}:
Beginning at 5th level, you can Attack twice, instead of once, whenever
you take the Attack action on Your Turn.
}
\newcommand{\DndClassAbilitySeven}{\textbf{Aura of Protection}:
Starting at 6th level, whenever you or a friendly creature within 10
feet of you must make a saving throw, the creature gains a bonus to the
saving throw equal to your Charisma modifier (with a minimum bonus of
+1). You must be conscious to grant this bonus. (Already included.)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Specialty
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndSpecialtyName}{Oath of the Ancients}
\newcommand{\DndSpecialtyPreamble}{\textbf{Oath of the Ancients}:
The tenets of the \emph{Oath of the Ancients} have been preserved for
uncounted centuries. This oath emphasizes the principles of good above
any concerns of law or chaos. Its four central principles are simple.
\begin{itemize}
\item
\textbf{Kindle the Light.} Through your acts of mercy, kindness, and
forgiveness, kindle the light of hope in the world, beating back
despair.
\item
\textbf{Shelter the Light.} Where there is good, beauty, love, and
laughter in the world, stand against the wickedness that would swallow
it. Where life flourishes, stand against the forces that would render it
barren.
\item
\textbf{Preserve Your Own Light.} Delight in song and laughter, in
beauty and art. If you allow the light to die in your own heart, you
can't preserve it in the world.
\item
\textbf{Be the Light.} Be a glorious beacon for all who live in despair.
Let the light of your joy and courage shine forth in all your deeds.
\end{itemize}
}
\newcommand{\DndSpecialtyAbilityOne}{\textbf{Channel Divinity}:
Your oath allows you to channel divine energy to fuel magical Effects.
Each Channel Divinity option provided by your oath explains how to use
it.\par
When you use your Channel Divinity, you choose which option to use. You
must then finish a short or Long Rest to use your Channel Divinity
again.\par
Some Channel Divinity Effects require Saving Throws. When you use such
an effect from this class, the DC equals your Paladin spell save
DC.
}
\newcommand{\DndSpecialtyAbilityTwo}{
\textbf{Channel Divinity, Nature's Wrath}: You can use your Channel
Divinity to invoke primeval forces to ensnare a foe. As an action, you
can cause spectral vines to spring up and reach for a creature within 10
feet of you that you can see. The creature must succeed on a Strength
or Dexterity saving throw (its choice) or be restrained.  While
restrained by the vines, the creature repeats the saving throw at the
end of each of its turns. On a success, it frees itself and the vines
vanish.
}
\newcommand{\DndSpecialtyAbilityThree}{
\textbf{Channel Divinity, Turn the Unholy}: As an action, you present
your holy symbol and speak a prayer censuring fiends and undead, using
your Channel Divinity. Each fiend or undead that can see or hear you
within 30 feet of you must make a Wisdom saving throw. If the creature
fails its saving throw, it is turned for 1 minute or until it takes
damage.\par
A turned creature must spend its turns trying to move as far away from
you as it can, and it can't willingly move to a space within 30 feet of
you. It also can't take reactions. For its action, it can use only the
Dash action or try to escape from an effect that prevents it from
moving. If there's nowhere to move, the creature can use the Dodge
action.\par
}
\newcommand{\DndSpecialtyAbilityFour}{
\textbf{Aura of Warding}: Beginning at 7th level, ancient magic lies so
heavily upon you that it forms an eldritch ward. You and friendly
creatures within 10 feet of you have resistance to damage from spells.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Attacks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndWeaponOneName}{Dawnbringer}
\newcommand{\DndWeaponOneType}{Str}
\newcommand{\DndWeaponOneDamageType}{radiant}
\newcommand{\DndWeaponOneDamage}{1d10}
\newcommand{\DndWeaponOneMagicToHit}{2}
\newcommand{\DndWeaponOneMagicDamage}{2}
\newcommand{\DndWeaponOneSpecailKey}{vs. undead}
\newcommand{\DndWeaponOneSpecailVal}{+1d8}

\newcommand{\DndWeaponTwoName}{greataxe}
\newcommand{\DndWeaponTwoType}{Str}
\newcommand{\DndWeaponTwoDamageType}{slashing}
\newcommand{\DndWeaponTwoDamage}{1d12}

\newcommand{\DndWeaponThreeName}{longbow}
\newcommand{\DndWeaponThreeType}{Dex}
\newcommand{\DndWeaponThreeDamageType}{piercing}
\newcommand{\DndWeaponThreeDamage}{1d8}

\newcommand{\DndWeaponFourName}{handaxe}
\newcommand{\DndWeaponFourType}{Str}
\newcommand{\DndWeaponFourDamageType}{slashing}
\newcommand{\DndWeaponFourDamage}{1d6}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Combat Special (box highlight)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndCombatSpecialOne}{
\textbf{Dawnbringer} appears to be a gilded longsword hilt. While
grasping the hilt, you can use a bonus action to make a blade of pure
radiance spring from the hilt, or cause the blade to disappear. If you
are proficient with shortswords or longswords, you are proficient with
Dawnbringer.
\begin{itemize}
\item While the blade exists, this magic longsword has the
\textit{finesse} property.
\item The sword's luminous blade emits bright light in a 15-foot radius
and dim light for an additional 15 feet. The light is sunlight. While
the blade persists, you can use an action to expand or reduce its radius
of bright and dim light by 5 feet each, to a maximum of 30 feet each or
a minimum of 10 feet each.
\item If you attune to Dawnbringer, you gain a +2 bonus to attack and
damage rolls made with her, which deals radiant damage instead of
slashing damage. When you hit an undead with it, that target takes an
extra 1d8 radiant damage.
\item Dawnbringer can communicate with its wearer telepathically. As
long as you are attuned to her, she knows every language you know.
Otherwise, she can speak and understand Common.
\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Class Specialty (box highlight)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\DndSpecialtyBoxHighlightOne}{
\textbf{Preacher's Pendant of Sending}: A small pendant on a string. It
is shaped like a scroll and can be unrolled a litttle, but is made from
fully black material. It requires attunement for it to have the
following effects:
\begin{itemize}
  \item You may add 5 ft to the range of your Channel Divinity.
  \item Once per long rest, you may cast \textit{Message}.
	  You do not need the material component for this spell.
\end{itemize}
}

% Note: Inventory is in a separate sheet document entirely
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% pull in all of the variables needed for everything else
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{dnd-ensure-variables}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End of global variables, beginning of layout
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fonts are hard, going with Alegreya for now:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[T1]{fontenc}
\usepackage{Alegreya} %% Option 'black' gives heavier bold face
\renewcommand*\oldstylenums[1]{{\AlegreyaOsF #1}} % cargo culting
\setlength\parindent{0pt} % we do not want to repeat \noindent everwhere
\begin{document}
\pagenumbering{gobble} % turn off pagenumbers
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% First Page, and flow to additional pages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\raggedright
\input{dnd-character-header-1}
\input{dnd-main-stats-and-traits}
% end stats, begin regular text-like layout
\newcommand{\DndSkipCombatSpecialSectionHeader}{1}
\input{dnd-combat-special}
\newcommand{\DndSkipRaceSectionHeader}{1}
\input{dnd-race-abilities}
\newcommand{\DndSkipClassAbilitiesSectionHeader}{1}
\input{dnd-class-abilities}
\newcommand{\DndSkipSpecialAbilitiesSectionHeader}{1}
\input{dnd-special-abilites}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header 2: new page for character physical stuff header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\raggedright
\input{dnd-character-header-2}
\input{dnd-background}
\fbox{\parbox{\textwidth}{
\textbf{Preacher's Pendant of Sending}:\par\framebox(15,10){} Once per
long rest, you may cast \textit{Message}. You do not need the material
component for this spell.\par
}}
\input{dnd-paladin-spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
